\documentclass{beamer}
\usetheme{Frankfurt}
\usepackage{color}
\usepackage{graphicx}
\usepackage[font=scriptsize,skip=1pt]{caption}
\usepackage{textpos}
\usepackage{multirow}
\usepackage{multicol}
%\usepackage{wrapfig}
\usepackage[labelformat=empty]{caption}
\usepackage[labelformat=empty,skip=0pt,justification=raggedright]{subcaption}
\usepackage{remreset}
\usepackage{multimedia}
\usepackage{mdframed}
\usepackage{natbib}
\usepackage[export]{adjustbox}

\definecolor{beaublue}{rgb}{0.74, 0.83, 0.9}
\definecolor{bubbles}{rgb}{0.91, 1.0, 1.0}
\definecolor{arsenic}{rgb}{0.23, 0.27, 0.29}
\definecolor{blizzardblue}{rgb}{0.67, 0.9, 0.93}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\definecolor{auburn}{rgb}{0.43, 0.21, 0.1}
\definecolor{applegreen}{rgb}{0.55, 0.71, 0.0}
\definecolor{camel}{rgb}{0.76, 0.6, 0.42}
\definecolor{scarlet}{rgb}{1.0, 0.13, 0.0}
\definecolor{shamrockgreen}{rgb}{0.0, 0.62, 0.38}
\definecolor{tiffanyblue}{rgb}{0.04, 0.73, 0.71}
\definecolor{saffron}{rgb}{0.96, 0.77, 0.19}
\definecolor{aphids}{rgb}{0.85, 0.85, 0.23}
\definecolor{dummy}{rgb}{0.6, 0.6, 0.99}
\definecolor{larvae}{rgb}{0.53, 0.53, 0.21}

\setbeamercolor{section in head/foot}{fg=arsenic, bg=bubbles}
%\setbeamercolor{subsection in head/foot}{fg=black, bg=babyblue}
\setbeamercolor{frametitle}{fg=auburn, bg=white}
\setbeamercolor{upper separation line head}{bg=airforceblue}
\setbeamertemplate{section in head/foot}{\insertsectionhead}

\makeatletter
\@removefromreset{subsection}{section}
\makeatother
\setcounter{subsection}{1}


\graphicspath{{./Figures/}}

 \title{An introduction to Bayesian Data Analysis using STAN}
 \subtitle{}
 
 \author{Lionel Hertzog \& Maxime Dahirel}
 
 \date{BDA workshop, BES-Gf\"{O}, Necov joint meeting, XX December 2017, Gent}
 
 


\begin{document}
 
 \frame{\titlepage}
 
\note{Who am I, recently started here, the aim of this talk is to show some on-going analysis and results from my PhD and also talk about ideas for this position.}
 
\begin{frame}
 \frametitle{\bf Structure of the workshop}
  \begin{enumerate}
   \item General introduction to Bayesian Data Analysis (circa. 30min)
   \item Examples of BDA workflow (circa. 30min)
   \item Small group discussion on specific themes (circa. 30min)
  \end{enumerate}

 
 \end{frame}
 
\begin{frame}
 \frametitle{\bf Structure of the talk}
  \begin{itemize}
   \item What is Bayesian Data Analysis
   \item How to do Bayesian Data Analysis
   \item Why do Bayesian Data Analysis
  \end{itemize}

 
 \end{frame} 
 
 
\section*{What?} 
 
 \begin{frame}
  \frametitle{\bf Why do we do Stats?}
  
  Some elements of inference, how does it fits into the science workflow
  
 \end{frame}

  \begin{frame}
  \frametitle{\bf Big world / small world}
  
  Our models have limited scope and only give answers within their area of expertise
  
 \end{frame}
 
  \begin{frame}
  \frametitle{\bf Bayesian data analysis in one formula}
  
  P (hypothesis given data) is prop to P(data givan hypothesis) * P(hypothesis) or
  Posterior  is prop to Likelihood * Prior
  
 \end{frame}
 
  \begin{frame}
  \frametitle{\bf What is Likelihood}
  
 \end{frame}
 
  \begin{frame}
  \frametitle{\bf What is prior infos}
  
 \end{frame}
 
  \begin{frame}
  \frametitle{\bf Whta is Posterior}
  
 \end{frame}
 
  \begin{frame}
  \frametitle{\bf It's all about uncertainty}
  
 \end{frame}
 
  
\section{How?}

 \begin{frame}
  \frametitle{\bf Ways to fit bayesian models in R}
  
  Coding in probability language vs using wrappers
  
 \end{frame}

  \begin{frame}
  \frametitle{\bf The sampling}
  
  Blind man in the likelihood landscape, how do we effectively sample it
  
 \end{frame}

  \begin{frame}
  \frametitle{\bf The sampling in BUGS and JAGS}
  
  Metropolis-Hasting sampling, adv. and dis.
  
 \end{frame}
 
  \begin{frame}
  \frametitle{\bf The sampling in STAN}
  
  Hamiltonian Monte Carlo, adv. and dis.
  
 \end{frame}
 
  \begin{frame}
  \frametitle{\bf Elements of bayesian vocabulary}
  
  Chains, convergence, divergence, Rhat, n\_eff, tree depth
  
 \end{frame}
 
  \begin{frame}
  \frametitle{\bf Model checking in Bayesian data analysis}
  
  convergence, n\_eff, chains, posterior predictive checks
  
 \end{frame}
 
  \begin{frame}
  \frametitle{\bf Model comparison}
  
  LOOC, WAIC ...
  
 \end{frame}
 

\section{Why?}
 
  \begin{frame}
  \frametitle{\bf Embracing uncertainty}
  
  Everything is variable, all parameters come with (posterior) distribution, can interprete posterior sample
  as probabilities, flexibility to test any hypothesis building on these
  
 \end{frame}
 
  \begin{frame}
  \frametitle{\bf Flexibility in model building}
  
  As long as you can write your likelihood function you can fit any model you like (similar to using MLE approach
  ie with bbmle)
  
 \end{frame}
 
  \begin{frame}
  \frametitle{\bf Why do we do stats?}
  
  Bayesian data analysis give us relevant answers in terms of probability rather than weird answers refering to som null hypothesis in
  terms of frequency
  
 \end{frame}
 
  \begin{frame}
  \frametitle{\bf No degrees of freedom}
  
  Fit complex models even with little data (is this something we want??)
  
 \end{frame}
 
  \begin{frame}
  \frametitle{\bf Asymptotic convergence, when bayesian and frequentist approach give similar answers}
  
  With infinite sample size the posterior distribution just reflect the likelihood, as sample size increases
  priors have dwindling effects
  
 \end{frame}
 
\end{document}

 \begin{frame}
  \frametitle{\bf }
  
 \end{frame}